\subsection{Entanglement}
Entanglement is a property of quantum systems that is the source of many of the remarkable results displayed by quantum algorithms. Essentially it is the presence of correlations in a quantum system that is stronger than possible classically. 
\begin{definition}[Separable Pure States]
    Consider two qubits $A$ and $B$, residing in Hilbert spaces $\mathcal{H}_A$, $\mathcal{H}_B$. Their composite state $\ket{\Psi}$ resides in the composite Hilbert space $\mathcal{H}_A \otimes \mathcal{H}_B$.
\end{definition}
\begin{definition}[Entangled States]
    Two qubits $A$ and $B$ are entangled if their composite state cannot be expressed as a seperable state.
\end{definition}
Generalising entanglement to higher dimensions in the context of this report is done by having entanglement between qudits as opposed to qubits. There is no requirement for the dimensions of the entangled qudits to be matching. For example,
\begin{equation}
    \ket{\psi} = \frac{1}{\sqrt{2}}\left(\ket{0}_2\otimes\left(\ket{+_0}_3\right) + \ket{1}_2\otimes\left(\ket{+_1}_3\right)\right),
\end{equation}
is a entangled state between a qubit and a qutrit ($d=3$).

\subsubsection{Measuring entanglement}
In order to analyse the efficiency of an entanglement transfer protocol, it is useful to have a method of quantifying entanglement.
Indeed, there are many different methods of quantifying entanglement, and there is no one standard method preferred above all others.
Here I introduce and define two common measures of entanglement.\newline

We first define \emph{von Neumann entropy}, $S$, used for pure states.
\begin{equation}
    S(\rho) = -\text{tr}(\rho \ln \rho),
\end{equation}
where $\rho$ is the density matrix representing the quantum system and $ln$ is the natural matrix logarithm. 
It is often easier to compute this quantity using the spectral decomposition of $\rho$,
\begin{equation}
    \rho = \sum_a \lambda_a \ket{a}\bra{a}.
\end{equation}
Using this form we can compute the entropy by
\begin{equation}
    S(\rho) = -\sum_a \lambda_a \ln\lambda_a.
\end{equation}
We define the \emph{ebit} as is the unit of bipartite entanglement. It is the entanglement contained in a Bell State \cite{Eisert_2000}. Maximally entangled states in $d \times d$ dimensions have $log_2(d)$ ebits.

Whilst QW dynamics are unitary, which ensures that pure states retain their purity as the walk progresses, we will see that this measure of entanglement is not appropriate for measuring how well our entanglement has been transferred as our protocol will also involve projections, which are not unitary.
To this end, we introduce an alternative measure of entanglement called \emph{negativity,} $\mathcal{N}$ \cite{Vidal_2002}.
\begin{equation}
    \mathcal{N}(\rho) = \frac{||\rho^{\Gamma_A}||_1-1}{2},
\end{equation}
where $\rho^{\Gamma_A}$ denotes the \emph{partial transpose} of $\rho$ with respect to the subsystem $\mathcal{H}_A$ and $||X||_1 = Tr(\sqrt{X^\dagger X})$ denotes the \emph{trace norm} of $X$.\newline

Similarly to von Neuman entropy, it is possible to rewrite this definition in terms of eigenvalues, this time eigenvalues of $\rho^{\Gamma_A}$,
\begin{equation}
    \mathcal{N}(\rho) = \sum_{\lambda_a < 0}|\lambda_a| = \sum_{\lambda_a} \frac{|\lambda_a| - \lambda_a}{2}.
\end{equation}